The \dealii Library, Version 9.6

### 2024-08-11 9.6/paper.tex
Fix name.
Add B. Blais to release 9.6 paper

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Marc Fehling,
    Johannes Heinz,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

@@

\begin{itemize}
\item non-nested multigrid: new features and performance improvement
\item FERemoteEvaluation
\item FEColungValues
  \todo[inline]{This can not be the right class name, it does not
    exist in deal.II.}
\end{itemize}

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Johannes Heinz,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[11]{Bruno Blais}
\affil[11]{Chemical Engineering High-performance Analysis, Optimization and Simulation (CHAOS) laboratory, Department of Chemical Engineering,
          Polytechnique Montréal,
          PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
          {\texttt{bruno.blais@polymtl.ca}}}

@@

\begin{itemize}
\item non-nested multigrid: new features and performance improvement
\item FERemoteEvaluation
\item FECouplingValues
\end{itemize}
